---
title: "R101"
author: "Iftakharul Alam"
date: '2021/11/28 (updated: `r Sys.Date()`)'
output:
  slidy_presentation: default
subtitle: Learning R 101
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      fig.align = "center", 
                      dpi = 100,
                      fig.height = 4.5)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

---

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

---

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

---

## Slide with Plot

```{r pressure}
plot(pressure)
```

---

## Polygon

```{r}
plot(x = c(1, 2, 4, 3, 1), y = c(2, 4, 3, 1, 2),
     ylab = "", xlab = "",
     main = "Polygon", type = "l")
```

---

## Polygon

```{r}
library(rnaturalearth)
library(sf)
library(dplyr)
poland_df <- ne_countries(type = 'countries', scale = 'small', returnclass = "sf") %>%
  filter(name == "Poland")
plot(poland_df$geometry, col = rgb(59, 132,86, maxColorValue = 255), border = 'grey', 
     axes = TRUE, main = "Poland")
```

---